---
title: "&gt; Meet the Toolkit"
author: "Gabriel E. Cabrera, M.Sc.<br><span style = 'font-size: 50%;'>Universidad de Chile<br>Master in Finance – Full Time</span>"
date: 'Fall 2022<br><br>`r icons::icon_style(icons::fontawesome("link", style = "solid"), scale = 1, fill = "white")` [bit.ly/2ObxeQa](https://bit.ly/2ObxeQa)<br>`r icons::icon_style(icons::fontawesome("twitter", style = "brands"), scale = 1, fill = "white")` [GabboCg](https://twitter.com/gabbocg)'
output:
  xaringan::moon_reader:
    chakra: libs/remark-latest.min.js
    css: [xaringan-themer.css, my-theme.css]
    nature:
      ratio: '14:9'
      countIncrementalSlides: false
      titleSlideClass: ["left", "middle", "inverse"]
      highlightLines: true
      highlightStyle: solarized-dark
    includes:
      in_header: header.html
---

layout: true
  
<div class="my-footer"><span><small>Introduction to Python for Finance • @GabboCg</small></span></div>

---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE, message = FALSE, dpi = 72)

library(icons)      ## for FontAwesome icons (ozunconf17 project!)
library(emo)       ## for emoji, obvs (github.com/hadley/emo)
library(tidyverse) ## for data wrangling
```

```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
mono_light(
  base_color = "#125972", ## picked to coordinate with rOpenSci logo
  code_highlight_color = "#c0e8f5",
  link_color = "#197b9e",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Droid Mono")
)
```

class: center, middle

<img style="border-radius: 50%; border:3px solid #ffffff;" src="https://avatars1.githubusercontent.com/u/35644280?s=400&u=67a633cb4550ad26715625df4b09ecc580677441&v=4" width="150px"/>

# You can find me at...

<a href="mailto:gcabrerag@fen.uchile.cl"><i class="fa fa-paper-plane fa-fw"></i>&nbsp;gcabrerag@fen.uchile.cl</a><br>
<a href="https://gcabrerag.rbind.io/"><i class="fa fa-link fa-fw"></i>&nbsp; gcabrerag.rbind.io</a><br>
<a href="https://twitter.com/GabboCg"><i class="fab fa-twitter"></i>&nbsp; @GabboCg</a><br>
<a href="http://github.com/GabboCg"><i class="fab fa-github"></i>&nbsp; @GabboCg</a><br>
<a href="http://pregrado.fen.uchile.cl/"><i class="fa fa-map-marker fa-fw"></i>&nbsp; School of Economics and Business, Universidad de Chile </a>

---

class: inverse, center, middle

#  Anaconda = Spyder + Python 

---

# [`r fontawesome::fa("fab fa-youtube", fill = "red")`](https://youtu.be/_bT30M4aBVM)  Installation

To install Anaconda you must follow these steps:

1. Go to [https://www.anaconda.com/](https://www.anaconda.com/)

2. Click on **Products** > **Individual Edition** > **Download**

3. Select the Anaconda **installer** (Graphical Installer) with Python 3.8 according to your operating system:

  * Windows `r fontawesome::fa("fab fa-windows")` 
  
  * MacOS `r fontawesome::fa("fab fa-apple")` 
  
  * Linux `r fontawesome::fa("fab fa-linux")` 

4. Follow the instructions for your operating system until the installation is complete.

5. To verify that Anaconda was installed correctly, click on the following link: [`r fontawesome::fa("fab fa-youtube", fill = "red")`](https://youtu.be/0dRb5wRjEq8)

---

class: inverse, center, middle

# Jupyter Notebooks 

---

# How to use Jupyter Notebook?

<br>
<center>
<iframe width="560" height="315"
src="https://www.youtube.com/embed/r58wn96Qd3c">
</iframe>
</center>

* Source: https://youtu.be/r58wn96Qd3c

---

class: inverse, center, middle

# Google Colab ☁️ + 💻

---

# [`r fontawesome::fa("fab fa-youtube", fill = "red")`](https://youtu.be/PZEHvgx06FE) How to use Google Colab?

1. An alternative to Spyder is Google Colab (.ipynb).

2. Colab lets you run and write Python<sup>1</sup> code in your browser:

  * No configuration required

  * Free access to GPUs

  * Easy sharing

3. To get started, go to https://colab.research.google.com/

4. Then click on Sign in (you may use your @fen.uchile.cl email)

5. To see Google Colab in action, click on `r fontawesome::fa("fab fa-youtube", fill = "red")` to the left of this *slide*'s title.

.footnote[

[1] It also supports other programming languages such as R or Julia 😱😱😱!!!.

]

---
class: center, middle, inverse

# Thank You Very Much

The slide theme was based on [Jennifer L Thompson](https://jenthompson.me/resources/).

Slides created via the R package [xaringan](https://github.com/yihui/xaringan).

The chakras come from [remark.js](https://remarkjs.com), [knitr](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

This work is licensed under a Creative Commons Attribution- ShareAlike 4.0 International License.

To view a copy of this license, visit:

https://creativecommons.org/licenses/by-sa/4.0/

